Material Metohds

### 2019-08-30 doc/MatMeth.Rmd
work on MM, added bibliography file

---
title: "Material Metohds"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
---

@@

1.	(Specific strains were obtained from X vendors, 2.
2.	3 separate rooms used (precautions taken to ensure there was limited environmental variance) b. X additional husbandry things done to help with breeding of some mouse strains. housed in X conditions (extra things done for problem breeders,
3.	3. euthanized under X protocol,

X mice used

@@

1.	describe how gonad tissue was collected)  (right testes, both ovaries) (tunica removed decapsulated)  X protocol for testes,   X protocol for ovaries.  X ages for males, X ages for females
2.	 2. describe spread process   (describe process - clearly point out the distinctions for testes and ovaries
3.	3. (describe staining process (with DMC1)  (same process)

@@

@@

>>>>

---
title: "Material Metohds"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_MatMeth.bib
---

@@

1.	(Specific strains were obtained from X vendors, 2.
2.	3 separate rooms used (precautions taken to ensure there was limited environmental variance) b. X additional husbandry things done to help with breeding of some mouse strains. housed in X conditions (extra things done for problem breeders,
3.	euthanized under X protocol,
4. mention results if there was a detectable environmental effect

The Wild derived inbred strains PWD/PhJ, PERC/Eij, WSB/EiJ, LEWE/EiJ, MSM/MsJ, MOLF/EiJ, CAST/EiJ, CZECHII/EiJ, CORLI/EiJ and SPRET/EiJ were purchased from Jax labs (Maine USA). 
The strains of KAZ/TUA, TOM/TUA, AST/TUA, HMI/TUA and SPIC) were ordered and cryo-derived from BRC at RIKEN (Japan) website). All mice were housed UW-Madison Biotech and MSC facilities - following the protocols.
 A breeding colony of wild derived mice sampled from Gough Island were housed at UW Veterinary school facilities.  (some of the other strains housed there - comparisons were made of strains housed across different facilities to (test if there was an effect of mouse room of MLH1 counts).

Mice were feed on dry standard breeder chow. Some strains sunflower seeds, nestlets and larger cages were added to improve fertility and litter survival. Adult mice were euthanized by CO asphyxiation. Neonate and embryonic mice were euthanized by decapitation following the protocols approved by the Institutional Animal Care and Use Committee at the University of Wisconsin-Madison.

@@

1.	describe how gonad tissue was collected)  (right testes, both ovaries) (tunica removed decapsulated)  X protocol for testes,   X protocol for ovaries.  X ages for males, X ages for females
2.	 describe spread process   (describe process - clearly point out the distinctions for testes and ovaries
3.	(describe staining process (with DMC1)  (same process)

From males, the right teste was collected and processed. (Ages are listed in supplmental material). Ovaries were collected from neonates less than 48 hours old or embryos between e16 to 21.

The behavior of these strains did not allow us to check for copulary plugs, resulting in most oocyte data coming from neonate mice between 5 to 48 hours.

Meiocyte spreads were made following  [@peters_1997] Peters et al 2001. For testes the tunica was removed and whole testes was incubated in 3ml of hypotonic solution for 45min. For ovaries after dissection, the pair of ovaries were decapsulated in cold PBS and both were incubated in 300ul of hypotonic solution for 45 min.

After incubation, gonads were transferred to sucrose solution -for mastication to make a cell slurry which was transferred to 80ul of 2% PFA solution. Cells were fixed in this solution and dried in a humid chamber at room temperature overnight. The next morning, slides were treated with a photoflow wash.

@@

Reprocessing in Photoshop ()- Image file names were anonymized before manual scoring of MLH1 or DMC1 foci.

@@

-hypothese tested (size, DSB number)

# References
